---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rstep: a workflow for STEP (Sahelian Transpiration Evaporation and Productivity) model under R

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/MadoShi64/rstep.svg?branch=master)](https://travis-ci.com/MadoShi64/rstep)
[![R-CMD-check](https://github.com/MadoShi64/rstep/workflows/R-CMD-check/badge.svg)](https://github.com/MadoShi64/rstep/actions)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/MadoShi64/rstep?branch=master&svg=true)](https://ci.appveyor.com/project/MadoShi64/rstep)
[![Codecov test coverage](https://codecov.io/gh/MadoShi64/rstep/branch/master/graph/badge.svg)](https://app.codecov.io/gh/MadoShi64/rstep?branch=master)
<!-- badges: end -->

rstep provides simple functions to automatize the different tasks when performing 1D or 2D STEP (Mougin et al. 1995) simulation. It prepares the input data (meteo (file.mto), sol (file.sol), animal load (file.cha), vegetation (file.veg)...) for STEP simulation, by cleaning and formatting the data. It provides a simple workflow for the model parametrization and calibration, with a set of functions to automatize the visualisation of the model outputs (1D: plots and 2D: maps), using several functions some of which come from other packages in the R environment. 

## Installation

The development version of rstep can be installed from GitHub:

``` r
install.packages("remotes")
remotes::install_github("MadoShi64/rstep")
```

## Some examples

Calling a STEP soil file for formatting

```{r}
rstep::sol
```


An example showing how to perform a linear regression, display the graph and metrics with one line of code (example with a random dataset.) 

```{r cars}
library(rstep)

set.seed(15)
var = abs(rnorm(30)) # observation
var.simu = abs(rnorm(30)) # simulation

# create data frame
data = data.frame(var,var.simu) 

# Plot the graph of the regression
step_reg(data,"var","plot")

# Check the metrics of the linear regression 
step_reg(data,"var","metric")

```

